### 2015-12-11 introduction.tex
minor removals of text

For unbounded decision sets no scale-free algorithm with a non-trivial regret
bound was known. Unbounded decision sets are practically important, since
learning large-scale linear models (e.g. logistic regression) can be reduced to
OLO with $\R^d$ as the decision set. One of our contributions is an
\textsc{FTRL}-based scale-free algorithm with a non-trivial regret bound for
any regularizer and any decision set, bounded or unbounded.

@@

Our proofs of the regret upper bounds rely on homogeneous inequalities
(Lemmas~\ref{lemma:recurrence-solution}, \ref{lemma:useful},
\ref{lemma:sum-of-square-roots-inverses}).  Previously, many proofs of regret
bounds relied on ad-hoc non-homogeneous inequalities, or the existing
algorithms used quantities (e.g.  $\sum_{t=1}^T \|\ell_t\|_*^2$) that are not
available until all loss vectors are processed. Two of the inequalities
(Lemmas~\ref{lemma:recurrence-solution} and \ref{lemma:useful}) are new and
interesting in their own right.

>>>>

For unbounded decision sets no scale-free algorithm with a non-trivial regret
bound was known. Unbounded decision sets are practically important, since
learning large-scale linear models (e.g. logistic regression) can be reduced to
OLO with $\R^d$ as the decision set.
% One of our contributions is an
% \textsc{FTRL}-based scale-free algorithm with a non-trivial regret bound for
% any regularizer and any decision set, bounded or unbounded.

@@

Our proof tecnique are also new because they rely on new homogeneous inequalities
(Lemmas~\ref{lemma:recurrence-solution}, \ref{lemma:useful},
\ref{lemma:sum-of-square-roots-inverses}).
% Previously, many proofs of regret
% bounds relied on ad-hoc non-homogeneous inequalities, or the existing
% algorithms used quantities (e.g.  $\sum_{t=1}^T \|\ell_t\|_*^2$) that are not
% available until all loss vectors are processed. Two of the inequalities
% (Lemmas~\ref{lemma:recurrence-solution} and \ref{lemma:useful}) are new and
% interesting in their own right.
